### 2018-11-30 manuscript/manuscript.rmd
facet figure of matrix clade composition

D=clade_rects(sequence_matrices[[1]])

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```

@@

matrix_overlap = 
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) matrix_overlap(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()

>>>>

taxon_rectangles = lapply(
	sequence_matrices,
	function ( sequence_matrix ){
		clade_rects(sequence_matrix)
	}
) %>%
	bind_rows()

ggplot(data=taxon_rectangles) + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
	facet_wrap( ~ manuscript_matrix )

@@

matrix_overlap = 
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) compute_matrix_overlap(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()
